Carbonate chemistry at Ny-Ålesund

### 2021-12-31 awipev-CO2.Rmd
Minor chnages in figs (using ggreg now) Also, deactivated chunk SNAPO

# make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_fb_mix_interp ,sal_fb_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_insitu_11m_mix,temp_insitu_11m_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
    sal_fb_mix_interp = mean(sal_fb_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_insitu_11m_mix = mean(temp_insitu_11m_mix, na.rm = TRUE),
    temp_insitu_11m_mix_interp = mean(temp_insitu_11m_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
  )

@@

### **Calculated vq Durafet**

@@

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
lm <- lm2(x = d_all$ph_s_sf_temp_insi, y = d_all$pHint_tot_sf)
p <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf, monthd) %>%
  tidyr::drop_na() %>%
  ggplot(aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8, 8.25), ylim=c(8, 8.25))+
  labs(x = "pH spectro", y = "pH seafet", color = "Months")
print(p)
```

@@

Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have
been flaged "3" by the SNAPO. After a close look, these samples are not
differents from their duplicates. Then we put the flag to "2" (good
result).

@@

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

pdelta_at_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    annotate("text", x = diff$datetime[17], y = 7, label = "4 µmoles/kg", color="red")+
    #annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
    labs(title= "AT", x="Time", y="Delta between TA replicates")+
    Mytheme()
pdelta_ct_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
    #annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
    labs(title= "CT",x="Time", y="Delta between CT replicates")+
    Mytheme()
p_ct_ts <- ggplot() +
    geom_point(data=discrete, aes(x= datetime, y= ct)) +
    labs(title= "",x="Time", y="CT (µmoles/kg)")+
    Mytheme()
p_at_ts <- ggplot() +
    geom_point(data=discrete, aes(x= datetime, y= at)) +
    labs(title= "",x="Time", y="AT (µmoles/kg)")+
    Mytheme()

@@

ct_diff_xts <- dplyr::select(diff, datetime, ct_diff, ct)
ct_diff_xts <- as.xts(ct_diff_xts, order.by = diff$datetime)
pdelta_ct_snapo_dygraph <- dygraph(ct_diff_xts, group = "awipev", main="Discrete CT (SNAPO) measurements", ylab="CT") %>%
    dySeries("ct_diff", label = "CT delta", color ="red", strokeWidth=0, pointSize=4) %>%
    dySeries("ct", label = "CT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
   dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#E0DEDE") %>%
  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#E0DEDE") %>%
  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#E0DEDE") %>%
  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C0C0") %>%
      dyShading(from = snapcoevents[13], to = snapcoevents[14], color = "#E0DEDE") %>%

  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
       dyLegend(show = "follow")   %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1), digitsAfterDecimal=2) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

# make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_fb_mix_interp ,sal_fb_mix,temp_fb, at_mean_interp, at, ct_mean_interp, ct, temp_insitu_11m_mix,temp_insitu_11m_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
    sal_fb_mix_interp = mean(sal_fb_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_insitu_11m_mix = mean(temp_insitu_11m_mix, na.rm = TRUE),
    temp_insitu_11m_mix_interp = mean(temp_insitu_11m_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
  )

@@

### **Calculated vs Durafet**

@@

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
reg <- ggreg(
  xdata = d_all$ph_s_sf_temp_insi,
  ydata = d_all$pHint_tot_sf,
  type = "MA",
  plot = TRUE,
  title = "pH spectro vs pH seafet (at in situ temperature)",
  xlab = "pH spectro",
  ylab = "pH seafet",
  proplot = TRUE
)
print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
```

@@

Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have
been flagged "3" by the SNAPO. After a close look, these samples are not
different from their duplicates. Then we put the flag to "2" (good
result).

@@

```{r SNAPO, eval =FALSE, echo=FALSE, message= FALSE, warning=FALSE}
# I THINK THIS CHUNK IS NO LONGER NEEDED AS THE REPLICATES HAVE ALREADY BEEN AVERAGED ABOVE.

# use the df at_ct for mean and sd
# create a new df to calculate the diff between replicate
diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))
pdelta_at_snapo <-ggplot() +
    geom_point(data = diff, aes(x = datetime, y = at_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    annotate("text", x = diff$datetime[17], y = 7, label = "4 µmoles/kg", color="red")+
    #annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
    labs(title= "AT", x="Time", y="Delta between TA replicates")+
    Mytheme()
pdelta_ct_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
    #annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
    labs(title= "CT",x="Time", y="Delta between CT replicates")+
    Mytheme()
p_ct_ts <- ggplot() +
    geom_point(data=discrete, aes(x= datetime, y= ct)) +
    labs(title= "",x="Time", y="CT (µmoles/kg)")+
    Mytheme()
p_at_ts <- ggplot() +
    geom_point(data=discrete, aes(x= datetime, y= at)) +
    labs(title= "",x="Time", y="AT (µmoles/kg)")+
    Mytheme()

@@

ct_diff_xts <- dplyr::select(diff, datetime, ct_diff, ct)
ct_diff_xts <- as.xts(ct_diff_xts, order.by = diff$datetime)
pdelta_ct_snapo_dygraph <-
  dygraph(ct_diff_xts,
          group = "awipev",
          main = "Discrete CT (SNAPO) measurements",
          ylab = "CT") %>%
  dySeries(
    "ct_diff",
    label = "CT delta",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dySeries(
    "ct",
    label = "CT duplicates",
    color =  "blue",
    strokeWidth = 0,
    pointSize = 2,
    axis = "y2"
  ) %>%
  # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#E0DEDE") %>%
  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#E0DEDE") %>%
  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#E0DEDE") %>%
  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C0C0") %>%
  dyShading(from = snapcoevents[13], to = snapcoevents[14], color = "#E0DEDE") %>%
  dyAxis(
    "y",
    axisLineColor = "red",
    label = "",
    axisLabelColor = "red",
    axisLineWidth = 5
  ) %>%
  dyAxis(
    "y2",
    axisLineColor = "blue",
    axisLabelColor = "blue",
    axisLineWidth = 5
  ) %>%
  dyLegend(show = "follow")   %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    digitsAfterDecimal = 2
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
